imputation

### 2019-03-18 imputation.Rmd
edit tables

---
title: "imputation"
author: "Jeremy Forbes"
date: "18/03/2019"
output: html_document
---

## Imputation
Methodology
- Not specific to electorates
- Explain spatial and then temporal

Applied to electorates
- For our models we use electorates
- Visualizations of an example using electorates
- Possible to use finer levels of disaggregation (e.g. SA1). Propose a cascading technique for reduced computation burden (SA4, SA3, SA2, SA1).

-------------------------------------------------------------------------------------

@@

```{r timeline, messages = F, echo = F, fig.cap="Timeline of Australian elections and Censuses. They do not always occur in the same year.", out.width = "90%", fig.align="center"}
library(tidyverse)
timeline <- data.frame(year = c(2001:2016)) %>%
  mutate(Election = ifelse(year %in% c(2001, 2004, 2007, 2010, 2013, 2016),1,0),
         Census = ifelse(year %in% c(2001, 2006, 2011, 2016), 1.4, 0)) %>%
  gather(c(Election,Census), key = event, value = measure) %>%  filter(measure != 0) %>%
  mutate(year_vis = ifelse(event == "Census", year + 0.1, year))

@@

```{r hume13, fig.cap = "Some of the electoral boundaries in NSW for 2013, with the electoral boundary for Hume, shown in purple."}
library(eechidna)
library(ggplot2)
library(ggthemes)
hume_area13 <- nat_map13 %>% 
  filter(state %in% c("ACT","NSW"), long < 154)

@@

Electorate (2016) | Percentage | Population in Electorate | Estimated Population Allocated to Purple Region [$\hat{P}_{s,t}$]
------------------|------------|--------------------------|------------------------------------------------
Hume              | 96.54%     | 150643                   | 145427
Riverina          | 25.11%     | 155793                   | 39117
Eden-Monaro       | 11.09%     | 147532                   | 16358
Canberra          | 0.28%      | 196037                   | 548
Fenner            | 0.23%      | 202955                   | 474
Whitlam           | 0.06%      | 152280                   | 92
Gilmore           | 0.06%      | 150436                   | 86
Calare            | 0.01%      | 161298                   | 21

@@

```{r eval = F, include = F}
library(knitr)
auscitizen_ex <- abs2016 %>% 
  filter(DivisionNm %in% c("HUME", "RIVERINA", "EDEN-MONARO", "CANBERRA", "FENNER", "WHITLAM", "GILMORE", "CALARE")) %>%
  select(DivisionNm, AusCitizen) %>% 
  mutate(`Estimated Population Allocated to Purple Region` = c(21, 548, 16358, 474, 86, 145427, 39117, 92),
    AusCitizen = round(AusCitizen, 2)) %>% 
  arrange(-`Estimated Population Allocated to Purple Region`)

@@

|DivisionNm  | AusCitizen (%): $D_s$| Estimated Population Allocated to Purple Region: $\hat{P}_{s,t}$|
|------------|---------------|------------------------------------------------|
|HUME        |          90.02|                                          145427|
|RIVERINA    |          89.11|                                           39117|
|EDEN-MONARO |          88.00|                                           16358|
|CANBERRA    |          85.48|                                             548|
|FENNER      |          83.64|                                             474|
|WHITLAM     |          89.52|                                              92|
|GILMORE     |          89.03|                                              86|
|CALARE      |          87.56|                                              21|

>>>>

---
title: "imputation"
author: "Jeremy Forbes"
date: "18/03/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(eechidna)
library(ggplot2)
library(ggthemes)
library(knitr)
```

@@

```{r timeline, message = F, echo = F, fig.cap="Timeline of Australian elections and Censuses. They do not always occur in the same year.", out.width = "90%", fig.align="center"}
timeline <- data.frame(year = c(2001:2016)) %>%
  mutate(Election = ifelse(year %in% c(2001, 2004, 2007, 2010, 2013, 2016),1,0),
         Census = ifelse(year %in% c(2001, 2006, 2011, 2016), 1.4, 0)) %>%
  gather(c(Election,Census), key = event, value = measure) %>%  filter(measure != 0) %>%
  mutate(year_vis = ifelse(event == "Census", year + 0.1, year))

@@

```{r hume13, fig.cap = "Some of the electoral boundaries in NSW for 2013, with the electoral boundary for Hume, shown in purple."}
hume_area13 <- nat_map13 %>% 
  filter(state %in% c("ACT","NSW"), long < 154)

@@

Electorate (2016) | Percentage | Population in Electorate | Estimated Population Allocated to Purple Region: $\hat{P}_{s,t}$
---------------------|------------|--------------------------|------------------------------------------------
HUME              | 96.54%     | 150643                   | 145427
RIVERINA          | 25.11%     | 155793                   | 39117
EDEN-MONARO       | 11.09%     | 147532                   | 16358
CANBERRA          | 0.28%      | 196037                   | 548
FENNER            | 0.23%      | 202955                   | 474
WHITLAM           | 0.06%      | 152280                   | 92
GILMORE           | 0.06%      | 150436                   | 86
CALARE            | 0.01%      | 161298                   | 21

@@

```{r eval = F, include = F}
auscitizen_ex <- abs2016 %>% 
  filter(DivisionNm %in% c("HUME", "RIVERINA", "EDEN-MONARO", "CANBERRA", "FENNER", "WHITLAM", "GILMORE", "CALARE")) %>%
  select(DivisionNm, AusCitizen) %>% 
  mutate(`Estimated Population Allocated to Purple Region` = c(21, 548, 16358, 474, 86, 145427, 39117, 92),
    AusCitizen = round(AusCitizen, 2)) %>% 
  arrange(-`Estimated Population Allocated to Purple Region`)

@@

|DivisionNm      | AusCitizen (%): $D_s$| Estimated Population Allocated to Purple Region: $\hat{P}_{s,t}$|
|----------------|----------------------|------------------------------------------------|
|HUME            |                 90.02|                                          145427|
|RIVERINA        |                 89.11|                                           39117|
|EDEN-MONARO     |                 88.00|                                           16358|
|CANBERRA        |                 85.48|                                             548|
|FENNER          |                 83.64|                                             474|
|WHITLAM         |                 89.52|                                              92|
|GILMORE         |                 89.03|                                              86|
|CALARE          |                 87.56|                                              21|
